\vfill A Testing Framework for Web Applications

### 2014-02-07 Paper/paper.tex
Rough Draft (Very rough...)

%%%%%%%%%%%%%%%%
%%% Abstract 
%%% VERY General overview of problem and solution in paper
%%%%%%%%%%%%%%%%
\begin{abstract}
Our framework is the best framework because we made it and we're awesome.
\end{abstract}

@@

\subsubsection{Acceptance Testing}
\todo{PUT INFO HERE PLEASE!!!}

@@

\subsubsection{``Finding Bugs In Dynamic Web Applications'' \cite{FindingBugs}}
Seven researchers from the MIT Computer Science and Artificial Intelligence Lab wrote a paper addressing testing in dynamic web applications. Common testing techniques were not made to work with dynamic content that can be generated at the drop of a hat or click of a button. Therefore, common testing techniques are inadequate for testing dynamic web applications. This paper discusses ways to find bugs in these new-fangled dynamic web applications. They use a new technique and extended a tool called Apollo. This technique generates dynamic test cases based on concrete and symbolic execution. “The basic idea is to execute an application on an initial input (e.g., an unconstrained or randomly chosen input), and then on additional inputs obtained by solving constraints derived from exercised control ﬂow paths.”

@@

\subsubsection{``Testing Web Services: A Survey'' \cite{TestingWebServicesSurvey}}
Three researchers at the Centre for Research on Evolution, Search \& Testing at King's College in London wrote a survey of web frameworks for testing web services. Their focus is on Service-Oriented Computing, a paradigm in which web sites or applications provide small pieces of functionality usable by ``anyone''. These services are then combined to create more fully featured applications.

\subsubsection{\cite{RESTfulFramework}}

@@

MORE MORE MORE MORE

>>>>

%%%%%%%%%%%%%%%%
%%% Abstract 
%%% VERY General overview of problem and solution in paper
%%%%%%%%%%%%%%%%
\begin{abstract}
We have brought together a number of testing tools from the web and created what we feel is a fully-featured, easy to use, testing framework for web applications.
\end{abstract}

@@

\subsubsection{Acceptance Testing}
Acceptance testing is testing to confirm that your product meets a certain specification. Often in the terms of software this is making sure that your software meets an SRS (Software Requirements Specification) or a customer's outlined expectations. Often this testing is performed by the user of the software or that customer that ordered the software, rather than the developers.

@@

\subsubsection{``Finding Bugs In Dynamic Web Applications'' \cite{FindingBugs}}
Seven researchers from the MIT Computer Science and Artificial Intelligence Lab wrote a paper addressing testing in dynamic web applications. Common testing techniques were not made to work with dynamic content that can be generated at the drop of a hat or click of a button. Therefore, common testing techniques are inadequate for testing dynamic web applications. This paper discusses ways to find bugs in these new-fangled dynamic web applications. They use a new technique and extended a tool called Apollo. This technique generates dynamic test cases based on concrete and symbolic execution. ``The basic idea is to execute an application on an initial input (e.g., an unconstrained or randomly chosen input), and then on additional inputs obtained by solving constraints derived from exercised control flow paths.''

@@

\subsubsection{``Testing Web Services: A Survey'' \cite{TestingWebServicesSurvey}}
Three researchers at the Centre for Research on Evolution, Search \& Testing at King's College in London wrote a survey of web frameworks for testing web services. Their focus is on Service-Oriented Computing, a paradigm in which web sites or applications provide small pieces of functionality usable by ``anyone''. These services are then combined to create more fully featured applications. What they note in particular is that when using web services, you rarely have access to the source code and must therefore black-box test them. Corollary to that is that you have to implicitly trust whoever made the service. They go through and discuss a number of frameworks and come to the conclusion that it's most certainly not a solved problem for the following reasons: The frequency of testing required, Testing without disrupting the operation of the service, Determining when testing is required and which operations need to be tested. Regarding the frequency of testing, web services often change in effort to make improvements, but those improvements can change the services and break tests. Testing without disrupting service is difficult because these services often limit accesses or simultaneous access of both a test and a running web application. Finally, determining when and what to test comes back to the trust issue. Some services provide their own testing metrics that include code coverage, number of tests, etc. But you have to trust that they are thoroughly testing whatever it may be.

\subsubsection{``A Framework for Testing RESTful Web Services'' \cite{RESTfulFramework}}
Two people from the University of Dakota School of Aerospace Studies outline a framework for testing RESTful web services. RESTful web services, short for Representation State Transfer, are, in the context of web applications, a name for web APIs that conform to a set of constraints. In particular they must offer four request methods: GET, POST, PUT, and DELETE. These methods generally connect to a database or other storage system in order to store, retrieve, or delete entries therein.

\todo{Finish reading this paper... My bad Dr. Haungs.}

@@
